---
title: "Candy Produc."
author: "Alex Paul"
date: "21/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##LOAD PACKAGES
```{r}
library(ggplot2)
library(tidyverse)
library(plotly)
```
##LOAD DATA
```{r}
candy <- read.csv("C:\\lex\\candy_production.csv")
# Take a look at the class of the dataset US_candy_production
str(candy)
View(candy)
# Assign more meaningful variable names
colnames(candy)<-c("Period","candy_production")

# Convert data into time series dataset
attach(candy)
candyts<-ts(candy_production,c(1972,1),c(2017,8),12)
str(candyts)
```
The candy production dataset provides monthly totals of US candy production, from 1972 to August 2017 as a percent of 2012 production. We have now successfully converted this dataset to a time series class therefore no further class or date manipulation is required.

#EDA

To perform exploratory data analysis, let's first review the data with summary statistics and plots in R.

```{r}
# Check for missing values
sum(is.na(candyts))

# Check the frequency of the time series data
frequency(candyts)

# Check the cycle of the time series
cycle(candyts)

# Review the summary statistics
summary(candyts)

# Plot the raw data using the base plot function
plot(candyts,xlab="Year", ylab = "Candy Production as (%) of 2012 Production",main="Monthly US Candy Production from 1972 to 2017")

```
```{r}
boxplot(candyts~cycle(candyts),xlab="Month", ylab = "Candy Production as (%) of 2012 Production" ,main ="Monthly US Candy Production from 1972 to 2017")

```

